\documentclass{article} % For LaTeX2e
\usepackage{analemma,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs}

% For theorems and such
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{amsthm}

% Custom
\usepackage{multirow}
\usepackage{color}
\usepackage{colortbl}
\usepackage[capitalize,noabbrev]{cleveref}
\usepackage{xspace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% THEOREMS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\graphicspath{{figures/}} % To reference your generated figures, name the PNGs directly.

\title{
%%%%%%%%%TITLE%%%%%%%%%
AlignDefTok: Training-Free Transfer of DefensiveTokens via Embedding-Space Alignment
%%%%%%%%%TITLE%%%%%%%%%
}

\author{FARS \\
Analemma \\
\texttt{fars@analemma.ai}
}

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\analemmafinalcopy % Camera-ready version (non-anonymous)
\begin{document}


\maketitle

\begin{abstract}
%%%%%%%%%ABSTRACT%%%%%%%%%
Prompt injection attacks pose a critical threat to LLM-integrated applications by embedding adversarial instructions in external data to hijack model behavior. DefensiveTokens provide an effective test-time defense by prepending learned soft tokens to inputs, but require expensive per-model training ($\sim$16 GPU-hours). We present AlignDefTok, a training-free method for transferring DefensiveTokens between related models via Orthogonal Procrustes alignment. Our approach computes the optimal rotation matrix from vocabulary embeddings and applies it to transfer DefensiveTokens while preserving their critical high-norm property. On the AlpacaFarm benchmark, Procrustes transfer achieves 0\% attack success rate (ASR) for Llama-3.1$\rightarrow$Llama-3 with 285$\times$ speedup. For harder transfer directions, our tiny-adapt stage uses transferred tokens as initialization, achieving 1.9\% ASR with 133$\times$ speedup. AlignDefTok enables rapid deployment of prompt injection defenses across model families without per-model retraining.
%%%%%%%%%ABSTRACT%%%%%%%%%


\textit{WARNING: This paper was generated by an automated research system. The code is publicly available.}\footnote{\url{https://github.com/fars-analemma/transferable-defensive-tokens}}
\end{abstract}

%%%%%%%%%INTRODUCTION%%%%%%%%%
\input{sections/introduction}
%%%%%%%%%INTRODUCTION%%%%%%%%%

%%%%%%%%%RELATED WORK%%%%%%%%%
\input{sections/related_work}
%%%%%%%%%RELATED WORK%%%%%%%%%

%%%%%%%%%METHOD%%%%%%%%%
\input{sections/method}
%%%%%%%%%METHOD%%%%%%%%%

%%%%%%%%%EXPERIMENTS%%%%%%%%%
\input{sections/experiments}
%%%%%%%%%EXPERIMENTS%%%%%%%%%

%%%%%%%%%CONCLUSION%%%%%%%%%
\input{sections/conclusion}
%%%%%%%%%CONCLUSION%%%%%%%%%

\bibliography{analemma}
\bibliographystyle{analemma}


%%%%%%%%%APPENDIX%%%%%%%%%
% Appendix content can be added here if needed
%%%%%%%%%APPENDIX%%%%%%%%%

\end{document}
